### 2014-05-21 concl.tex
Add discussion

\chapter*{Conclusion}
\addcontentsline{toc}{chapter}{Conclusion}%

>>>>

\chapter{Discussion}

The practical impact of Sprout and Remy so far remains
preliminary. There have been several experiments on Sprout conducted
by companies interested in using it as a control algorithm for
videoconferencing or screen-sharing software. Generally speaking, I understand these
experiments have confirmed the ones in this thesis, under
the assumption that Sprout's request for bytes from the application
can always be satisfied.

However, in practice, coupling Sprout to an actual video coder has
presented several new challenges. Real video coders generally do not
have the agility to produce frames of exactly the requested coded
size, immediately on demand. Today's videoconferencing applications
typically allow the video coder to ``drive'' the application, coding and
sending video at a particular nominal bit rate until the transport
receives definitive evidence of congestion. Flipping that around---so
that Sprout's stochastic forecasts can ``drive'' the video
coder---may require changes to the video coder to be able to vary
the coded size of frames more rapidly.

As for Remy, much remains unknown about the capabilities and limits of
computer-generated algorithms, much less decentralized algorithms that
cooperate indirectly across a network to achieve a common
goal. Although the RemyCCs appear to work well on networks whose
parameters fall within or near the limits of what they were prepared
for---even beating in-network schemes at their own game and even
when the design range spans three orders of magnitude---our ability to reason about \emph{why} they
work is limited.

We can observe apparent limit cycles with the Ratatouille tool in
simulation and make some statements about the behavior of RemyCCs on
new kinds of simulated networks, but we do not have a principled
method to predict a RemyCC's performance on real-world heterogeneous
networks with unknown link parameters, topology, and cross-traffic.
Indeed, we have yet to run RemyCCs on real-world networks at all.

Along with the rigor of the computer-generated approach come new
challenges for protocol designers, who must figure out how to encode
their intuitions about the problem into an explicit statement of
assumptions and an objective. How should a protocol designer come up
with their model of the uncertain network? Our learnability
experiments in Chapter~\ref{chap:learnability} suggest that, even on
networks with more-complex structure, it may be sufficient for a
RemyCC to have been designed for the link rate and degree of
multiplexing of its \emph{bottleneck} link only. Much work needs to be
done, however, before we can reliably extrapolate from results on a
two-bottleneck parking-lot topology to more-complex networks. It may
also be possible for a RemyCC to ``learn'' different congestion
policies for different remote IP addresses, but the cross-interaction
between such adaptive RemyCCs---who might be executing different
policies at runtime---will need to be studied.

It was a surprising result that computer-generated end-to-end RemyCCs
were able to outperform some of the most sophisticated human-designed
in-network schemes, including Cubic-over-sfqCoDel and XCP. On the one
hand, this result is encouraging---it indicates that end-to-end
algorithms are more powerful than was previously understood,
perhaps making it possible to preserve a ``dumb'' network with smart endpoints.

In general, though, an in-network algorithm that can run on the
bottleneck gateway and enforce fairness among flows (as sfqCoDel and
XCP both do) is strictly more powerful than a decentralized algorithm
that runs purely end-to-end. My colleagues and I have
argued~\cite{sivaraman2013no} that, like endpoint congestion-control
schemes, in-network algorithms will need to keep evolving with time. I
expect that if similar methods to Remy are applied to the development
of in-network algorithms, they will be able to reclaim their
superiority over the best end-to-end algorithms.

### 2014-05-21 remy_eval.tex
Add discussion

\item {\bf Cellular wireless:} We used the Saturator traces (Section~\ref{ss:saturator}) of the
  Verizon and AT\&T LTE cellular services. We recreated these
  links within ns-2, queueing packets until they are released to the
  receiver at the same time they were released in the trace. This
  setup partly probes the RemyCC's resilience to ``model mismatch'' --- in
  both the Verizon and AT\&T traces, throughput and round-trip time
  strayed outside the limits of the RemyCC design range.

@@

We are interested in the end-to-end delay as well; the reasoning
behind Remy's objective function and the $\delta$ parameter is that
protocols that fill up buffers to maximize throughput are not as
desirable as ones that achieve high throughput \emph{and} low delay
--- both for their effect on the user, who may prefer to get his
packets to the receiver sooner, as well as any other users who share
the same FIFO queue.

@@

The schemes that require in-network assistance (XCP and
Cubic-over-sfqCoDel, shown in green) achieve higher throughput than
the TCPs, but less than the two more throughput-conscious
RemyCCs.\footnote{It may seem surprising that sfqCoDel, compared with
  DropTail, \emph{increased} the median RTT of TCP Cubic. CoDel drops
  a packet at the front of the queue if all packets in the past 100~ms
  experienced a queueing delay (sojourn time) of at least 5~ms. For
  this experiment, the transfer lengths are only 100~kilobytes; with a
  500 ms ``off'' time, such a persistent queue is less common even
  though the mean queueing delay is a lot more than 5 ms. DropTail
  experiences more losses, so has lower delays (the maximum queue size
  is $\approx 4\times$ the bandwidth-delay product), but also lower
  throughput than CoDel. In other experiments with longer transfers,
  Cubic did experience lower delays when run over sfqCoDel instead of
  DropTail.} This result is encouraging, because it suggests that even
a purely end-to-end scheme can outperform well-designed algorithms
that involve active router participation.  This demonstrates that
distributed congestion-control algorithms that explicitly maximize
well-chosen objective functions can achieve gains over existing
schemes.  As we will see later, however, this substantially better
performance will not hold when the design assumptions of a RemyCC are
contradicted at runtime.

In Figures~\ref{f:tpdelaydb4} and \ref{f:tpdelaydb8}, the RemyCCs do
not simply have better median performance --- they are also more fair
to individual flows, in that the performance of an individual sender
(indicated by the size of the ellipses) is more consistent in both
throughput and delay.

@@

To explain this result, we investigated how multiple RemyCC flows
share the network. We found that when a new flow starts, the system
converges to an equitable allocation quickly, generally after little
more than one RTT. Figure~\ref{f:trace} shows the sequence of
transmissions of a new RemyCC flow that begins while sharing the link.
Midway through the flow, the competing traffic departs, allowing
the flow to start consuming the whole bottleneck rate.

@@

The results are shown in Figure~\ref{f:spec}. On the particular link
for which the ``1$\times$'' RemyCC was designed, it performs the best,
but its performance trails off quickly around that value. Within the
range of the ``10$\times$'' RemyCC, it beats Cubic-over-sfqCoDel, but
again deteriorates when the true network violates its design
assumptions. The results show that more-specific prior knowledge is
helpful and improves performance --- when it happens to be correct.

>>>>

\item {\bf Cellular wireless:} We used the Saturator traces (Section~\ref{ss:saturator}) of the
  Verizon and AT\&T LTE cellular services. We recreated these
  links within ns-2, queueing packets until they are released to the
  receiver at the same time they were released in the trace. This
  setup partly probes the RemyCC's resilience to ``model mismatch''---in
  both the Verizon and AT\&T traces, throughput and round-trip time
  strayed outside the limits of the RemyCC design range.

@@

We are interested in the end-to-end delay as well; the reasoning
behind Remy's objective function and the $\delta$ parameter is that
protocols that fill up buffers to maximize throughput are not as
desirable as ones that achieve high throughput \emph{and} low
delay---both for their effect on the user, who may prefer to get his
packets to the receiver sooner, as well as any other users who share
the same FIFO queue.

@@

The schemes that require in-network assistance (XCP and
Cubic-over-sfqCoDel, shown in green) achieve higher throughput than
the TCPs, but less than the two more throughput-conscious
RemyCCs.\footnote{It may seem surprising that sfqCoDel, compared with
  DropTail, \emph{increased} the median RTT of TCP Cubic. CoDel drops
  a packet at the front of the queue if all packets in the past 100~ms
  experienced a queueing delay (sojourn time) of at least 5~ms. For
  this experiment, the transfer lengths are only 100~kilobytes; with a
  500 ms ``off'' time, such a persistent queue is less common even
  though the mean queueing delay is a lot more than 5 ms. DropTail
  experiences more losses, so has lower delays (the maximum queue size
  is $\approx 4\times$ the bandwidth-delay product), but also lower
  throughput than CoDel. In other experiments with longer transfers,
  Cubic did experience lower delays when run over sfqCoDel instead of
  DropTail.} This result is encouraging, because it suggests that even
a purely end-to-end scheme can outperform well-designed algorithms
that involve active router participation.  This demonstrates that
distributed congestion-control algorithms that explicitly maximize
well-chosen objective functions can achieve gains over existing
schemes.  As we will see in Section~\ref{s:oprangeperftradeoff}, this
substantially better performance will not hold when the design
assumptions of a RemyCC are contradicted at runtime.

@@

In Figures~\ref{f:tpdelaydb4} and \ref{f:tpdelaydb8}, the RemyCCs do
not simply have better median performance: they also give more
consistent throughput and delay to individual flows. To explain this
result, we investigated how multiple RemyCC flows share the
network. We found that when a new flow starts, the system converges to
an equitable allocation quickly, generally after little more than one
RTT. Figure~\ref{f:trace} shows the sequence of transmissions of a new
RemyCC flow that begins while sharing the link.  Midway through the
flow, the competing traffic departs, allowing the flow to start
consuming the whole bottleneck rate.

@@

The results are shown in Figure~\ref{f:spec}. On the particular link
for which the ``1$\times$'' RemyCC was designed, it performs the best,
but its performance trails off quickly around that value. Within the
range of the ``10$\times$'' RemyCC, it beats Cubic-over-sfqCoDel, but
again deteriorates when the true network violates its design
assumptions. The results show that more-specific prior knowledge is
helpful and improves performance---when it happens to be correct.
